---
title: "week 4 part 1"
author: "Travis Christy"
date: "11/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

One Sampe T-Test Instructions: type: ?t.test in the console
Two sample T Test Instructions: typ

## 1. Confidence intervals

```{r}
otter_length <- c(34, 41, 50, 27, 32, 41, 48, 60, 43)

t.test(otter_length)
```
This is a look at a sample, not the whole population. Therefore there is a measure of uncertainty.
We're 95% sure that the mean will fall within the confidence interval shown above.



## T-test (1-sample t-test)

See a claim: mean otter length is 50 inches

```{r}
otter_test <- t.test(x = otter_length, mu = 50)
otter_test
```

P value of .040 means there is a 4.0 % chance that a random sample taken from the total population is at least as different from 50 in either direction as our sample mean.

More often when we do T-tests we are comparing two sample sets. We want to know if the sample means represent that they were drawn from the same population,

## two sample t-test

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x = desert_bighorns, y = sierra_bighorns)
```

confidence interval 1 is a negative value because of differences (y-x or x-y) in means but not typically reported
hypothesis is that the true difference in means in not = 0 
p value in a two sample t-test is the probability that your two samples were drawn from a population with the same mean. In this case that is 88.5%.





